### 2020-04-30 README.Rmd
a bit wider still

```{r draw-gam-figure, dev = "png", fig.height = 6, fig.width = 8, echo = FALSE, fig.show = "hide", message = FALSE}
df <- gamSim(eg = 1, n = 400, verbose = FALSE)
m <- gam(y ~ s(x0) + s(x1) + s(x2) + s(x3), data = df, model = "REML")
draw(m)
```

```{r appraise-figure, dev = "png", fig.height = 6, fig.width = 8, echo = FALSE, fig.show = "hide"}
appraise(m)
```

>>>>

```{r draw-gam-figure, dev = "png", fig.height = 6, fig.width = 9, echo = FALSE, fig.show = "hide", message = FALSE}
df <- gamSim(eg = 1, n = 400, verbose = FALSE)
m <- gam(y ~ s(x0) + s(x1) + s(x2) + s(x3), data = df, model = "REML")
draw(m)
```

```{r appraise-figure, dev = "png", fig.height = 6, fig.width = 9, echo = FALSE, fig.show = "hide"}
appraise(m)
```
